Optimal Algorithms for Dynamic Balanced Graph Partitioning

### 2020-05-14 paper/disc20clustering.tex
Comment

The algorithm in this section and the algorithm for $k=3$ (cf. Section~\ref{sec:k3}) are modified versions of the algorithm DET from~\cite{repartition-disc}.
The difference is in the choice of partition after a~component merge.
In DET, the partition was arbitrary.
In the algorithm for the learning model,
we choose a~component respecting partition closest to the initial partition.
In the algorithm from Section~\ref{sec:k3}, we choose the partition closest to the current partition (a repartition of minimum cost).
A generic sketch of these two algorithms can be found in the appendix (Algorithm \ref{alg:ppl}).

\noindent
\textbf{Perfect Partition Learner algorithm.}
Fix the initial partition
$P_I :=\{ I_1, \dots, I_{\ell}\}$ and \OPT's final partition
$P_F := \{F_1, \dots, F_{\ell}\}$.
The \emph{distance} of a~partition
 $P = \{C_1, \dots, C_{\ell}\}$ from the initial partition,
defined as 
$\Delta(P) := \sum_{j=1}^{\ell} | C_j \setminus I_j |$,
 is the number of nodes in $P$ that do not reside in their initial cluster.
In other words,
at least $\Delta(P)$ node migrations are required in order to reach the partition $P$ from $P_I$, and thus
$\OPT \geq \Delta^*:= \Delta(P_F) $.
%We  use $ \Delta(P_F) $ wherever the initial partition is clear from the context
The scheme of the algorithm can be found in the  appendix (Algorithm \ref{alg:ppl}).

>>>>

The algorithm in this section and the algorithm for $k=3$ (cf. Section~\ref{sec:k3}) are modified versions of the algorithm DET from~\cite{repartition-disc}.
The difference is in the choice of partition after a~component merge.
In DET, the partition was arbitrary.
In the algorithm for the learning model,
we choose a~component respecting partition closest to the initial partition.
In the algorithm from Section~\ref{sec:k3}, we choose the partition closest to the current partition (a repartition of minimum cost).
A generic sketch of these two algorithms can be found in the appendix (Algorithm \ref{alg:ppl}) \maciek{We don't have the generic. Also in the next paragraph you refer to the code}.

\noindent
\textbf{Perfect Partition Learner algorithm.}
Fix the initial partition
$P_I :=\{ I_1, \dots, I_{\ell}\}$ and \OPT's final partition
$P_F := \{F_1, \dots, F_{\ell}\}$.
The \emph{distance} of a~partition
 $P = \{C_1, \dots, C_{\ell}\}$ from the initial partition,
defined as 
$\Delta(P) := \sum_{j=1}^{\ell} | C_j \setminus I_j |$,
 is the number of nodes in $P$ that do not reside in their initial cluster.
In other words,
at least $\Delta(P)$ node migrations are required in order to reach the partition $P$ from $P_I$, and thus
$\OPT \geq \Delta^*:= \Delta(P_F) $ \maciek{Confusing. We have space. First define :=, then say that OPT bounds}.
%We  use $ \Delta(P_F) $ wherever the initial partition is clear from the context
The scheme of the algorithm can be found in the  appendix (Algorithm \ref{alg:ppl}).
